Enhancement of SDR in Thessaloniki

### 2024-09-11 GHI_enh_04_investigate.tex
Commit 2024-09-11 10:14

lmY: 109.4004 +/- 12.63018

@@

\caption{ - empty caption - }\label{fig:P-energy-complete-multi-1}
\end{figure}

@@

@@

\begin{verbatim}
2024-09-11 05:57:13.1 athan@sagan GHI_enh_04_investigate.R 1.539943 mins
\end{verbatim}

>>>>

lmY: 108.9825 +/- 13.53098

@@

\caption{ - empty caption - }\label{fig:P-energy-complete-multi-1}
\end{figure}
\begin{figure}[H]

@@

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-3}

\caption{ - empty caption - }\label{fig:P-energy-complete-multi-3}
\end{figure}

{\centering \includegraphics[width=1\linewidth]{GHI_enh_04_investigate_files/figure-latex/P-energy-complete-multi-4}

\caption{ - empty caption - }\label{fig:P-energy-complete-multi-4}
\end{figure}
\begin{figure}[H]

@@

\begin{verbatim}
2024-09-11 07:08:04.1 athan@sagan GHI_enh_04_investigate.R 1.522287 mins
\end{verbatim}
